---
title: Title of my report
format:
  manuscript_template-pdf: default
cite-method: natbib
author:
  - name: Jane Doe
    url: https://example.com
    orcid: 0000-0000-0000-0000
    affiliations:
      - id: some-inst
        name: Institute for Cool Things
        url: https://example.com
      - id: some-uni
        name: University of Awesome Research
        url: https://example.com
    email: corresponding email
  - name: John Doe
    affiliations:
      - ref: some-inst 
address:
  - code: a
    address: Institute of Smoke and Magic, University of Sometown, Sometown, XY, 12345
  - code: b
    address: Department of Neat Tricks, Whereever State University, Someplace, MC, 67890
# Optional: line of arbitrary text with additional information.
#date_subtitle: Published in *Journal of Statistical Software*, 2018
lead_author_surname: Jane Doe and John Doe
doi_footer: "Course ID"
abstract: |
  Your abstract will be typeset here, and used by default a visually distinctive font.
  An abstract should explain to the general reader the major contributions of the article. 
# Optional: Acknowledgements
acknowledgements: |
  This template package builds upon, and extends, the work of the excellent
  gratefully acknowledged as this work would not have been possible without them.  Our extensions
  are under the same respective licensing term
  [rticles](https://cran.r-project.org/package=rticles) package, and both packages rely on the
  [PNAS LaTeX](http://www.pnas.org/site/authors/latex.xhtml) macros. Both these sources are
  ([GPL-3](https://www.gnu.org/licenses/gpl-3.0.en.html) and
  [LPPL (>= 1.3)](https://www.latex-project.org/lppl/)).
# Optional: One or more keywords
keywords:
  - one
  - two
  - optional
  - keywords
  - here
papersize: letter
fontsize: 11pt
linkcolor: "0000FF"
headercolor: "000000"
# Optional: Force one-column layout, default is two-column
#manuscript_mode: true
# Optional: Enables lineno mode, but only if manuscript_mode mode is also true
#lineno: true
# Optional: Enable one-sided layout, default is two-sided
#one_sided: true
# Optional: Enable section numbering, default is unnumbered
#numbersections: true
# Optional: Specify the depth of section number, default is 5
#secnumdepth: 5
# Optional: Skip inserting final break between acknowledgements, default is false
skip_final_break: true
# Optional: Bibliography 
bibliography: bibliography.bib
# Optional: Enable a 'Draft' watermark on the document
#watermark: true
footer_contents: "Short Title"
editor: 
  markdown: 
    wrap: 72
---

## Introduction

This is a document template made with _pandoc_. It uses [markdown](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet) to format text. Go to this [link](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet) to see some more markdown tips on how to format.

I suggest that you use [Zotero](https://www.zotero.org) as your citation manager. Then you can export your citation library into a BibTex file (`.bib`). You can cite any paper that has an entry into the `bibliography.bib` file of this directory by typing `@` and enter the short "_`@`-code_" for that citation [@Tyagi1996]. Entering the citation into a sentence without brackets will cite it within the sentence, like this: "_As has been pointed out by @Tyagi1996 ..._". If you want multiple citations within a single paranthesis you simply enter them after each other with a semicolon (`;`) separating each citation [@Dussoix1962; @Tyagi1996; @Sanger1977]. I would also recommend the [doi2bib.org](https://www.doi2bib.org/) website wher eyou can simply paste in a DOI and get the corresponding BibTeX  entry to copy and paste into your `.bib` file.

## Author Affiliations

Per common academic best practice, you can include your department,
institution, and complete address, with the ZIP/postal code, for each
author. Use lower case letters to match authors with institutions, as
shown in the example. Authors with an ORCID ID may supply this
information at submission.

## Document Options

We support several options via the YAML header

-   Line of custom text in subtitle (`date_subtitle`) suitable to give
    publication info of the draft, e.g. journal name in a post-print;
-   Document date that appears in the footer can be specified manually
    using `document_date`.


## Inline R Code

You can directly enter R code and generate plots or figures directly in the document. If you dont want to show the code block generating the figure you simply set **`echo=FALSE`** for that code block. 

Here I'm loading the `ggplot` package and then I use some sample data that comes with R to plot a scatterplot with `ggplot` 

```{r figex, fig.width=3, fig.height=3, cache=TRUE, echo=TRUE, fig.cap="**This plot shows a scatterplot.** If you would have multiple panels. **a)** You can simply describe them here. **b)** and here. **c)** Also like this."}
library(ggplot2)
ggplot(mtcars, aes(wt, mpg)) +
    geom_point(size=3, aes(colour=factor(cyl))) +
    theme(legend.position="none")
```

There are some additional settings for the figure:

-   figure width and height (`fig.width`, `fig.height`), both set to
    three inches;
-   the caption (`fig.cap`) lets you add a custom caption for your figure. You dont have to keep track of your figure numbers since this is automatically updated.

## Digital Figures

Markdown, Pandoc and LaTeX support `.eps` and `.pdf` files.

Figures and Tables should be labelled and referenced in the standard way
using the `\label{}` and `\ref{}` commands.

The R examples above show how to insert a column-wide figure. To insert
a figure wider than one column, please use the
`\begin{figure*}...\end{figure*}` environment.

One (roundabout) way of doing this is to *not* actually plot a figure,
but to save it in a file as the following segment shows:

```{r densityPlot, echo=TRUE}
library(ggplot2)
p <- ggplot(data = midwest,
            mapping = aes(x = area,
                          fill = state,
                          color = state)) +
    geom_density(alpha = 0.3)
## save to file
suppressMessages(ggsave("densities.pdf", p))
```

This file is then included via standard LaTeX commands.

```{=tex}
\begin{figure*}
  \begin{center}
    \includegraphics[width=0.66\textwidth, height=3.5in]{densities} 
  \end{center}
  \caption{Wide ggplot2 figure}\label{fig}
\end{figure*}
```
## Typeset Code (But Do Not Run It)

We can also just show code.

``` r
xx <- faithful[,"eruptions"]
fit <- density(xx)
plot(fit)
```

This simply used a pandoc bloc started and ended by three backticks,
with `r` as the language choice. Similarly, *many* other languages can
be typeset directly simply by relying on pandoc.

## Single column equations

Authors may use 1- or 2-column equations in their article, according to
their preference.

To allow an equation to span both columns, options are to use the
`\begin{figure*}...\end{figure*}` environment mentioned above for
figures. The `\begin{widetext}...\end{widetext}` environment as shown in
equation \ref{eqn:example} below is deprecated, but \LaTeX commands
`\onecolumn` and `\twocolumn` work fine.

Please note that this option may run into problems with floats and
footnotes, as mentioned in the [cuted package
documentation](http://texdoc.net/pkg/cuted). In the case of problems
with footnotes, it may be possible to correct the situation using
commands `\footnotemark` and `\footnotetext`.

```{=tex}
\begin{equation}
  \begin{aligned}
(x+y)^3&=(x+y)(x+y)^2\\
       &=(x+y)(x^2+2xy+y^2) \\
       &=x^3+3x^2y+3xy^3+x^3. 
       \label{eqn:example} 
  \end{aligned}
\end{equation}
```
```{=html}
<!-- pandoc writes all tables using longtable, which fails in 2-column mode

  Species                    CBS     CV     G3
  ----------------------- ------ ------ ------
  1\. Acetaldehyde           0.0    0.0    0.0
  2\. Vinyl alcohol          9.1    9.6   13.5
  3\. Hydroxyethylidene     50.8   51.2   54.0

  : Comparison of the fitted potential energy surfaces and ab initio
  benchmark electronic energy calculations

-->
```
